A Survey of Range-Only SLAM Techniques and Sensors

### 2018-11-07 Paper.tex
Very very minor edits
Just some very slight grammer edits on the introduction

		The task of Simultaneous Localization and Mapping (SLAM) is a common aspect in many robotics applications. SLAM involves estimating the pose of a robot while simultaneously building a map of its environment with no priori knowledge of said environment. This task can be represented as a causality dilemma, where the pose of the robot is ascertained with respect to a global frame, or map, and the creation of a map requires knowledge of the robot's pose. There are a variety algorithms used to solve this problem, many of which use a landmark-based approach. Landmarks are distinguishable feature in an environment which can be observed via devices such as a camera or laser rangefinder. Said devices can be used to measure propeties such as the distance or orientation of the landmark relative to the robot. As the robot traverses the environment it continues to observe and collect landmarks while simultaneously building a map and localizing itself within the map. The sensed distance and orientation from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map. 
		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map. 
		In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.

		%A bit of a jarring transition. The goal is to introduce RO-SLAM and explain the difference between RO-SLAM and SLAM. The paragraph acomplishes that but maybe there is a smoother way to go about it. Also might need an explanation of location information and specifically how it differentiates from distance information
		In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) readings are used in addition to the vehicle's odometry. %ADD A CITATION
		While GPS has low resolution, it proves useful as it provides location information, which can help compensate for the accumulated error from drift in odometric sensors. However, GPS isn't available in all environments, such as indoors and underwater. Instead, wireless signals and sonar beacons are often used in indoors and underwater environments, respectively. These beacons provide distance estimations to the robotic vehicle, but do not inherently provide location information as with GPS. However, these distances are often still useful as they can be used to compensate for the drift that occurs from measuring a vehicle's displacement through integration of inertial sensor readings. Most SLAM algorithms utilize these range values as a corrective measurement, the same way traditional algorithms use sensed landmarks. However, rather than using range and orientation to landmarks, beacons are only capable of providing range. SLAM algorithms which utilize these beacons are referred to as Range-Only SLAM (RO-SLAM).

>>>>

		The task of Simultaneous Localization and Mapping (SLAM) is a common aspect in many robotics applications. SLAM involves estimating the pose of a robot while simultaneously building a map of its environment with no priori knowledge of said environment. This task can be represented as a causality dilemma, where the pose of the robot is ascertained with respect to a global frame, or map, and the creation of a map requires knowledge of the robot's pose. There are a variety algorithms used to solve this problem, many of which use a landmark-based approach. Landmarks are distinguishable feature in an environment which can be observed via devices such as a camera or laser rangefinder. Said devices can be used to measure propeties such as the distance or bearing of the landmark relative to the robot. As the robot traverses the environment it continues to observe and collect landmarks while simultaneously building a map and localizing itself within the map. The sensed distance and bearing to each landmark can be combined with other factors like odometry readings to get an refined estimation of the robot pose and map. 
		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map. 
	%	In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.

		%Ohhhh my good  this feels so jaring to read. I don't think odometry was ever properly introduced either
		In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) measurements are used to help localize a vehicle. %ADD A CITATION
		While GPS has low resolution, it proves useful as it provides location information, which can help compensate for the accumulated error from drift in odometric sensors. However, GPS isn't available in all environments, such as indoors and underwater. Instead, wireless signals and sonar beacons are often are utilized. These beacons provide range data, but do not inherently provide location information as with GPS. However, these distances are often still useful as they can be used to compensate for the drift that occurs from measuring a vehicle's displacement through integration of inertial sensor readings. Most SLAM algorithms utilize these range values as a corrective measurement, the same way traditional algorithms use sensed landmarks. However, rather than using range and orientation to landmarks, beacons are only capable of providing range. SLAM algorithms which utilize these beacons are referred to as Range-Only SLAM (RO-SLAM).
